### 2023-08-22 application.tex
up

\begin{theorem}\label{SL int-VASS}
{\sc Resilience} is decidable for integer VASS when $\Safe$ and $\Bad$ are semilinear.
\end{theorem}

@@

The above results concern only unbounded resilience. We consider now 
{\sc Bounded resilience} and {\sc $k$-resilience}, and focus on the length of
the path from $\Bad$ to $\Safe$
when $\Safe$ is downward-closed. Unfortunately, we have the following:
% \alain{incohérence des notations: VASS ou vector addition system with states and plus bas seulement vector addition system ??? VAS ???}
\begin{proposition}
{\sc Bounded resilience} and {\sc $k$-resilience} never hold for VAS when $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{proposition}

@@

\begin{theorem}
{\sc $k$-resilience }  and {\sc Bounded resilience} in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ are decidable%, and moreover {\sc $k$-resilience } is in $\EXPSPACE$
.
\end{theorem}

>>>>

\begin{theorem}\label{SL int-VASS}
{\sc Resilience} is decidable for integer VASS when $\Safe$ %and $\Bad$ are
is a
semilinear set.
\end{theorem}

@@

The above results concern only unbounded resilience. We consider now 
{\sc Bounded resilience} and {\sc $k$-resilience}, and focus on the length of
the path from $\Bad$ to $\Safe$
when $\Safe$ is downward-closed. Unfortunately, we have the following:
% \alain{incohérence des notations: VASS ou vector addition system with states and plus bas seulement vector addition system ??? VAS ???}
\begin{proposition}
{\sc Bounded resilience} and {\sc $k$-resilience} never hold for VAS when $\Safe = \downarrow \Safe$% and $\Bad = \uparrow \Bad$
.
\end{proposition}

@@

\begin{theorem}
{\sc $k$-resilience }  and {\sc Bounded resilience} are decidable for VASS when 
$\Safe = \downarrow \Safe$%
%$\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ are decidable%, and moreover {\sc $k$-resilience } is in $\EXPSPACE$
.
\end{theorem}
